---
title: "STAT 33B Lab Workbook WK 8"
date: "Mar 7, 2021"
author: "Won Shil Park (3033452021)"
output: pdf_document
---

This workbook is due __Mar 11, 2021__ by 9:00am or, if you attend lab, by Mar 12 11:59pm PT.


Workbooks are graded for completeness, so as long as you make a clear effort to
solve each problem, you'll get full credit. That said, make sure you understand
the concepts here, because they're likely to reappear in homeworks, quizzes,
and later lectures.

As you work, write your answers in this notebook. Answer questions with
complete sentences, and put code in code chunks. You can make as many new code
chunks as you like.

* Knit and submit the generated PDF file on Gradescope.



Default Arguments
=================

Watch the "Default Arguments" lecture video.


## Exercise 1

Write a function `to_kelvin()` to convert temperatures in degrees Celsius to
temperatures in degrees Kelvin (you can find the formula online). Your function
should have a parameter `celsius` for the temperature to convert.

Make sure that your function is vectorized in `celsius`, so that it can convert
an entire vector of temperatures in one call.

Show that your function works correctly for a few test cases.

**YOUR ANSWER GOES HERE:**


```{r}
to_kelvin = function(celsius) {
  celsius + 273.15
}

to_kelvin(numeric(0))
to_kelvin(0)
to_kelvin(c(0, 20, 100))
```



Function Example
================

The "Function Example" lecture video is optional. It provides a more realistic
example of writing a function.

No exercises for this section.



Variable Scope & Lookup
=======================

Watch the "Variable Scope & Lookup" lecture video.

No exercises for this section.



Lazy Evaluation
===============

Watch the "Lazy Evaluation" lecture video.

```{r}
# simplified the body since it's simple
# default is something that doesn't exit = masking
# error out since jasdfl doesn't exist when x = jasdfl in parameters
func = function(y = x, x) {
  x = 2
  y
}

func(x = 1)
```

## Exercise 2

Extend your `to_kelvin()` function to be able to convert degrees Fahrenheit to
degrees Kelvin as well. Add a parameter `fahrenheit` for the Fahrenheit
temperature to convert.

Leave the code in the body of your function unchanged. Instead, provide a
default argument for `celsius` that converts the `fahrenheit` argument.

Show that your function works correctly for a few test cases (for both Celsius
and Fahrenheit temperatures).

What happens if you call your function with arguments to the `celsius`
parameter and the `fahrenheit` parameter at the same time?
$$celsius = \frac{5}{9}(fahrenheit - 32)$$

**YOUR ANSWER GOES HERE:**

```{r}
to_kelvin = function(celsius = (fahrenheit - 32) * 5/9, fahrenheit) {
  celsius + 273.15
}

to_kelvin(celsius = c(0, 20, 30, 100))
to_kelvin(fahrenheit = c(32, 68, 86, 212))
to_kelvin(0, 10)
to_kelvin(celsius = 0, fahrenheit = asdfa)
```

Calling the version of the `to_kelvin()` function above with both arguments
converts only the `celsius` argument. The `fahrenheit` argument is completely
ignored.

_Depending on how you wrote `to_kelvin()`, your version might have different
results._



## Exercise 3

Rather than using a separate parameter in `to_kelvin()` for each source unit, a
better design is to have a `temperature` parameter and a `unit` parameter. The
function can then check `unit` and choose an appropriate conversion for
`temperature`.

The `unit` parameter should be restricted to supported units, which in this
case are `"celsius"` and `"fahrenheit"`. You can use the special `match.arg()`
function to check that an argument matches against a set of candidate
arguments. For instance, `match.arg(x, c("red", "blue"))` checks that the
argument to `x` is either `"red"` or `"blue"`. The function also allows for
partial matches, so for instance `"r"` matches `"red"`. See the documentation
for full details.

Rewrite the `to_kelvin()` function with a `temperature` and `unit` parameter.
Make sure the function is still vectorized in the `temperature` parameter.

As always, show that your function works correctly for a few test cases.

**YOUR ANSWER GOES HERE:**


```{r}
to_kelvin = function(temperature, unit) {
  unit = match.arg(unit, c("celsius", "fahrenheit"))
  if (unit == 'fahrenheit') {
    temperature = (temperature - 32) * 5/9
  }
  temperature + 273.15
}

to_kelvin(c(0, 20, 30, 100), "c")
to_kelvin(c(32, 68, 86, 212), "fahrenheit")
```



The Dots Parameter
==================

Watch the "The Dots Parameter" lecture video.

No exercises for this section.


Using Functions
===============

Watch the "Using Functions" lecture video.

No exercises for this section.
