---
title: "STAT 33A/B Lab Workbook Wk 13"
date: "Apr 16, 2021"
author: "Won Shil Park (3033452021)"
output: pdf_document
---

This workbook is due __Apr 22, 2020__ by 9:00am or by midnight Apr 23 if you attend lab.

* Knit and submit the generated PDF file on Gradescope.

For each of the following exercises, use the dogs data.

```{r}
load(url("http://www.stat.berkeley.edu/users/nolan/data/dogs.rda"))
```

```{r}
library(dplyr)
```



## Exercise 1

For each of the following tasks, show the code to compute the result:

+ Using base R
+ Using dplyr


1. The mean and median of the longevity column (ignoring missing values).

2. The subset that contains rows 10-20 of the height, weight, and longevity
   columns.

3. The number of dog breeds with weight greater than 42.

4. The subset of large dogs that require daily grooming.



### Part 1

```{r}
# Base R
mean(dogs$longevity, na.rm = TRUE)
median(dogs$longevity, na.rm = TRUE)

# dplyr
summarize(dogs, mean(longevity, na.rm = TRUE))
summarize(dogs, median(longevity, na.rm = TRUE))
```

### Part 2

```{r}
# Base R
dogs[10:20, c("height", "weight", "longevity")]

# dplyr
select(slice(dogs, 10:20), height, weight, longevity)
```

### Part 3

```{r}
# Base R
sum(dogs$weight > 42, na.rm = TRUE)

# dplyr
summarise(dogs, sum(weight > 42, na.rm = TRUE))
count(dogs, weight > 42)
```

### Part 4

```{r}
# Base R
dogs[dogs$size == "large" & dogs$grooming == "daily" & !is.na(dogs$grooming),]
subset(dogs, size == "large" & grooming == "daily")

# dplyr
filter(dogs, size == "large" & grooming == "daily")

```


## Exercise 2

Use dplyr and the dogs data to determine which 3 dogs cost the most.

Your answer to this exercise should be a data frame with 3 rows.



```{r}
sorted = arrange(dogs, desc(price))
slice(sorted, 1:3)

```





## Exercise 3

Use dplyr to answer each of the following:

1. On average, which `group` of dog has the highest lifetime cost? Which has
   the lowest?

2. How many dogs are there for each possible combination of `size` and
   `grooming`?



### Part 1

```{r}
groups = group_by(dogs, group)
costs = summarize(groups, mean_cost = mean(lifetime_cost, na.rm = TRUE))
arrange(costs, mean_cost)
```

You should find that herding dogs have the highest average lifetime cost. Working dogs have the lowest.

### Part 2


```{r}
count(dogs, size, grooming)
summarize(group_by(dogs, size, grooming), n = n())

```
