---
title: "STAT 33B Lab Workbook Wk 10"
date: "Mar 28, 2021"
author: "Won Shil Park (3033452021)"
output: pdf_document
---

This workbook is due __Apr 1, 2021__ by 9:00am PT or by midnight Apr 2 if you are attending lab.

* Knit and submit the generated PDF file on Gradescope.



## Exercise 1

A vectorized implementation of the `to_kelvin` function is:
```{r}
to_kelvin = function(temperature, unit) {
  unit = match.arg(unit, c("celsius", "fahrenheit"), several.ok = TRUE)

  # First convert Fahrenheit to Celsius.
  is_f = unit == "fahrenheit"
  temperature[is_f] = (temperature[is_f] - 32) * 5 / 9

  temperature + 273.15
}
```

Write a modified version of `to_kelvin` that checks for potential problems. In
particular, your version should check the assumptions that:

* `temperature` is numeric.
* `temperature` and `unit` are the same length, or `unit` has length 1.

Your version should raise an error (with a descriptive message) if either of
these assumptions don't hold.

Test your function to show that it checks for potential problems. You can use
`error = TRUE` on an RMarkdown code chunk to allow errors when knitting.

**YOUR ANSWER GOES HERE:**

```{r}
to_kelvin = function(temperature, unit) {
  if (!is.numeric(temperature)) {
    stop("temperature needs to be numeric")
  }
  
  if (length(temperature) != length(unit) && length(unit) != 1) {
    stop("temperature and unit need to be same length or unit needs to be length 1")
  }
  
  unit = match.arg(unit, c("celsius", "fahrenheit"), several.ok = TRUE)

  # First convert Fahrenheit to Celsius.
  is_f = unit == "fahrenheit"
  temperature[is_f] = (temperature[is_f] - 32) * 5 / 9

  temperature + 273.15
}
```


Test your function with the following inputs:
```{r, error = TRUE}
to_kelvin(c(0, 32, 212, 100), c("c", "f", "f", "c"))

to_kelvin(c(0, 100), "c")

to_kelvin("hello", "c")

to_kelvin(c(10, 20), c("c", "c", "f"))
```




## Exercise 2

getwd()
path.expand("~")
Skim `?options` and `?Startup`.

Create or edit your `.Rprofile` file to set an option (or several options).

Check that your option is actually set when you restart R (you can call
`options` without any arguments to see your current options).

In your answer here, describe which option you set and include the code you
added to `.Rprofile`.

**YOUR ANSWER GOES HERE:**
I used "options(prompt = ">>> ", continue = "... ")". Thus my regular "> " in my output turned into ">>> ".

My code looked like this:

> getwd()

> file.edit(".Rprofile)

In Rprofile tab I put in:

> options(prompt = ">>> ", continue = "... ")
