---
title: "STAT 33B Lec Workbook Wk 11"
date: "Apr 3, 2021"
author: "Won Shil Park (3033452021)"
output: pdf_document
---

This workbook is due __Apr 7, 2021__ by 11:59pm PT.

* Knit and submit the generated PDF file on Gradescope.


File Formats
=================

## Exercise 1
The `volerup.txt` file that contains the volcano data can be found in bcourses in the "data" directory. Download the file to your local computer and inspect it with a plain text editor to confirm the file format.

Read the data set into R as a data frame. Use both `read.delim()` and `read.csv()` and `read.table()`  to read the data into R.
Save each data frame into `vol.delim`, `vol.csv`, and `vol.table`, respecitvely.

The data frames should have 36 columns and 835 rows/eruptions.
You may need to provide arguments to the function calls, in addition to the location of the file. 

_HINT: Consider the values for the 'header', 'sep', and 'quote' parameters in your function calls._


```{r}
vol.delim = read.delim("~/Downloads/volerup.txt")
vol.csv = read.csv("~/Downloads/volerup.txt", sep = "\t")
vol.table = read.table("~/Downloads/volerup.txt", header = TRUE, sep = "\t", quote = "\"")
```

Confirm that the three data frames have the same dimension, and that they columns are of the same class. Are these three data frames identical?
 

```{r}
# check dim
dim(vol.delim)
dim(vol.csv)
dim(vol.table)

# check names
names(vol.delim)
names(vol.csv)
names(vol.table)

# check if identical
identical(vol.delim, vol.csv)
identical(vol.delim, vol.table)
```



## Exercise 2

Write the `vol.delim` data freme out as a CSV file called `vol2.csv`.
use the function `write.csv()` to do this.



```{r}
write.csv(vol.delim, file = "~/Downloads/vol2.csv", row.names = FALSE)
```

Read the csv file that you created back into R and save it as `vol2.csv`.
Use `identical()` to confirm that `vol2.csv` hasn't changed from `vol.delim`. If it has, investigate what changed, and fix your 
call by specifying alternative values to some of the parameters.

```{r}
vol.csv2 = read.csv("~/Downloads/vol2.csv")

identical(vol.csv2, vol.delim)
dim(vol.csv2)
names(vol.csv2)
```

