---
title: "STAT 33B Lec Workbook WK 8"
date: "Mar 7, 2021"
author: "Won Shil Park (3033452021)"
output: pdf_document
---

This workbook is due __Mar 10, 2021__ 11:59pm


Workbooks are graded for completeness, so as long as you make a clear effort to
solve each problem, you'll get full credit. That said, make sure you understand
the concepts here, because they're likely to reappear in homeworks, quizzes,
and later lectures.

Last week, we wrote a function, called `traceMean()` that takes the mean of values 
above a certain cut-off. We added parameters, threshold and dropNA to the function 
in order to specify the threshold and whether or not to drop NAs in calculating the mean.

Below is the function that we wrote in lecture. 

```{r}
traceMean = function (x, traceAmt, dropNA)
{
  if (!is.numeric(x)) {
    return(NA)
  } 
  mean(x[x > traceAmt], na.rm = dropNA)
}
```
```{r}
#lecture notes
xtest = c(0, 5, 10, NA, 20, 30, NA, NA)
traceMean(xtest, 5, FALSE)
traceMean(xtest, 5, TRUE)
```

This week, we will modify the function in the following ways:

1. Provide a default value for `traceAmt` so that it doesn't need to be specified in the call. Copy the function above into the code chunk below and modify it.

```{r}
traceMean = function (x, traceAmt = 0, dropNA)
{
  if (!is.numeric(x)) {
    return(NA)
  } 
  mean(x[x > traceAmt], na.rm = dropNA)
}

traceMean
```

Test your function.
```{r}
traceMean(xtest, dropNA = TRUE)
traceMean(xtest, 5, dropNA = TRUE)
# parameters doesn't have to be in order if you specify
traceMean(traceAmt = 5, xtest, dropNA = TRUE)
```

2. Add a `...` parameter to the function's signature and remove the `dropNA` parameter so that the user can simply pass the `na.rm = TRUE` or `na.rm = FALSE` in the function call.  Copy the function from step 1 into the code chunk below and modify it.

```{r}
traceMean = function (x, traceAmt = 0, ...)
{
  if (!is.numeric(x)) {
    return(NA)
  } 
  mean(x[x > traceAmt], ...)
}


```

Test your function.
```{r}
xtest = c(0, 5, 10, NA, 20, 30, NA, NA, 0, 5, 10, 0, 5, 10, 0, 5, 10, 1000, -2000)

traceMean(xtest, na.rm = TRUE, trim = 0.1)
# trim = takes vector 'xtest' and takes out 10% of each end since trim = 0.1
```

3. Allow the user to supply an alternative function to `mean()`. To do this, add a parameter called `FUN` and give it a default value of the mean function. Since the 
function has significantly changed, rename it to `traceSummary()`
Copy the function from step 2 into the code chunk below and modify it.

```{r}
traceSummary = function (x, traceAmt = 0, FUN = mean, ...)
{
  if (!is.numeric(x)) {
    return(NA)
  } 
  FUN(x[x > traceAmt], ...)
}


```


Use the following code chunks to test your function.

+ Use `traceSummary()` to compute the `median` of the values in `z` above 0 for and where NAs are removed. The answer should be 30.

```{r}
z = c(-1, 0, NA, 0, 100, 50, 30, 10, 10, 17, 20, 110, 60, NA)

traceSummary(z, na.rm = TRUE)
traceSummary(z, 0, na.rm = TRUE, trim = 0.2)
traceSummary(z, FUN = median, na.rm = TRUE)
```


+ Use `traceSummary()` to compute the 5% trimmed `mean` of the values in z that are greater than 10 and where NAs are removed. The answer should be about 55.3

```{r}
traceSummary(z, 10, na.rm = TRUE, trim = 0.05)
```

+ Use `traceSummary()` to compute `quantile` statistics of `z` values above 0. Pass into the function values for the `digits` and `na.rm` parameters. 

```{r}
traceSummary(z, FUN = quantile, na.rm = TRUE, digits = 2)
traceSummary(z, FUN = quantile, na.rm = TRUE, probs = c(.3, .6))
```

