---
title: "STAT 33B Lec Workbook WK 9"
date: "Mar 14, 2021"
author: "Won Shil Park (3033452021)"
output: pdf_document
---

This workbook is due __Mar 17, 2021__ 11:59pm


Workbooks are graded for completeness, so as long as you make a clear effort to
solve each problem, you'll get full credit. That said, make sure you understand
the concepts here, because they're likely to reappear in homework, quizzes,
and later lectures.

Below are the code snippets from the preallocation video.

The first loop does not preallocate.

```{r}
n = 20 
x = c()
      for (i in 1:n) {
        x = c(x, i * 2)
      }
x
length(x)
```

The next loop does preallocate.

```{r}
n = 20
x = numeric(n)
for (i in seq_len(n)) {
  x[i] = i * 2
}

x
```


## Step 1

If you haven't done so already, install the microbenchmark package.
Examine the signature of the  `microbenchmark()` function.
Notice that the first parameter is `...` for supplying the expressions 
to benchmark.

Call `mcirobenchmark()` with the two versions of the code. 
Repeat the evaluation of the code 50 times and ask for the results to be 
in microseconds, i.e., set the `unit` parameter value to "ms".
Note that you need only call `microbenchmark()` once, passing in the two 
versions of the code. Make sure to wrap each version in curly braces.
Also, there's no need to supply `n` in the call. It can be set once outside the call. 

```{r}
library(microbenchmark)
n = 20
microbenchmark({x = c()
      for (i in 1:n) {
        x = c(x, i * 2)
      }}, 
{x = numeric(n)
for (i in seq_len(n)) {
  x[i] = i * 2
}}, 
times = 50L, unit = "ms")
```


## Step 2

Wrap your call to `microbenchmark()` into a function called `benchit()`.
The parameters to this function should be

- n - the length of the vector x; make this a required argument
- times - the number of times the expressions are run; set the default to 50L 

```{r}
benchit = function(n, rep = 50L) {
  microbenchmark({x = c()
      for (i in 1:n) {
        x = c(x, i * 2)
      }}, 
{x = numeric(n)
for (i in 1:n) {
  x[i] = i * 2
}}, 
times = rep, unit = "ms")
}

```


Call `benchit()` with `n = 20` and assign the return value to `b`.
Use `class()` to confirm that `b` is a data frame.
What is its dimension? Variable names?

```{r}
b = benchit(n = 20)

class(b)

names(b)

sapply(b, class)

dim(b)
head(b$time)
tail(b$time)
head(b)
```

## Step 3

Use `tapply()` with `b` to compute the median time for each expression.

```{r}
tapply(b$time, b$expr, median)


```


## Step 4

Now let's benchmark for vectors of length  10, 100, 1000, and 10000.
If 10000 is too slow for your computer then you can reduce the value.

+ Create a vector called `n` with these 4 values.
+ Preallocate a vector twice the length of n to store the median times for the two approaches. Call this vector `meds`.
+ Write a for loop to call `benchit()` for each `n` and assign the median times for the two approaches into `meds`.

Hint: We recommend using `seq_along` in the for loop.

```{r}
n = c(10, 100, 1000, 10000)
meds = numeric(2 * length(n))

for (i in seq_along(n)) {
  b = benchit(n = n[i])
  meds[c((2 * i - 1), (2*i))] = c(tapply(b$time, b$expr, median)[1], 
                      tapply(b$time, b$expr, median)[2])
  
}
meds
```

How much faster is preallocation when `n` is 10000? How do the two methods compare for the different values of n? To make this comparison divide the median times for the first strategy by the preallocation strategy (e.g., divide the first element of `meds` by the second, the third by the fourth, and so on). Note this can be done as a vectorized calculation. 

```{r}
meds[seq(1, 8, by = 2)] / meds[seq(2, 8, by = 2)]

 
```



