---
title: "STAT 33A/B Lec Workbook Wk 13"
date: "Apr 17, 2021"
author: "Won Shil Park (3033452021)"
output: pdf_document
---

This workbook is due __Apr 19, 2021__ by 11:59pm PT for STAT 33A and 
__Apr 21, 2021__ by 11:59pm PT for STAT 33B.


* Knit and submit the generated PDF file on Gradescope.


## Exercise 1

How many packages are in the Tidyverse? Explore the website to find out. You
can count the tidymodels packages as a single package.

**YOUR ANSWER GOES HERE:**
There are 8 core packages in the tidyverse.
In addition, there are another 12 or so packages for a total of about 20 packages. 


## Exercise 2

1. Read the documentation for the tibble package on the website. What's the
   name of the function that creates a new tibble from column vectors?

2. Create a tibble with 4 rows and 3 columns. You can make up the data in the
   columns, but use a different data type for each one.

3. Show how to convert the tibble from step 2 into an ordinary data frame.




### Part 1
The tibble() function is used to create a tibble from vectors. 
Each vector should be the same length and will be used to create a column in the tibble.


### Part 2



```{r}
library(tibble)

tb = tibble(x = 1:4, y  = c(TRUE, TRUE, FALSE, TRUE), z = c("a", "bb", "ccc", "dddd"))

class(tb)

df = data.frame(x = 1:4, y  = c(TRUE, TRUE, FALSE, TRUE), z = c("a", "bb", "ccc", "dddd"))

class(df)

df
tb
```

### Part 3

```{r}
tb2 = as.data.frame(tb)

class(tb2)
```




## Exercise 3

Use dplyr and the dogs data to compute each of the following subsets:

1. Rows 10-30 only

2. All rows except row 51

3. All columns except `popularity_all` and `popularity`

4. Rows 1-10 with only the `breed`, `weight`, and `height` columns


You do not need to print out these subsets, just show us the code to compute
them.


```{r}
load(url("http://www.stat.berkeley.edu/users/nolan/data/dogs.rda"))
```




### Part 1

Here the results are hidden so that the solutions PDF doesn't have pages and
pages of raw data printouts.

```{r, results = "hide"}
library(dplyr)

tb1 = slice(dogs, 10:30)
tb1

df1 = dogs[10:30, ]
df1
```


### Part 2

```{r, results = "hide"}
tb2 = slice(dogs, -51)

df2 = dogs[-51, ]

dim(tb2)

tb2[50:52, 1:4]
dogs[50:52, 1:4]
df2[50:52, 1:4]
```

### Part 3

```{r, results = "hide"}
tb3 = select(dogs, -popularity_all, -popularity)

tb3a = select(dogs, -"popularity_all", -"popularity")

tb3b = select(dogs, -c(4,5))
  
df3 = dogs[ , !(names(dogs) %in% c("popularity_all", "popularity"))]

df3a = dogs[ , -c(4, 5)]

names(df3a)

```

### Part 4

```{r}
tb4 = slice(select(dogs, breed, height, weight), 1:10)
tb4a = select(slice(dogs, 1:10), breed, height, weight)
df4 = dogs[1:10, c("breed", "height", "weight")]

df4
```


## Exercise 4

Use dplyr to show that there are no duplicated rows in the dogs data.

Explain your reasoning.

```{r}
dim(distinct(dogs))
dim(dogs)
dim(dogs) == dim(distinct(dogs))
```


## Exercise 5

Use dplyr to determine for each `group` of dog, what's the shortest lifespan? 
You should have one result per group here. 

Additionally, for each `group` of dog, what's the longest lifespan?


Here are the shortest lifespans for each group of dog:
```{r}
groups = group_by(dogs, group)
summarize(groups, short.life = min(longevity, na.rm = TRUE))

```

Here are the longest lifespans for each group of dog:
```{r}
summarize(groups, long.life = max(longevity, na.rm = TRUE),
          avg.wt = mean(weight, na.rm = TRUE), ct = n(), first.dog = first(breed))

```

An alternative approach to subsetting
```{r}
tb5 = filter(dogs, group == "toy")

df4 = dogs[dogs$group == "toy", ]

dim(tb5)
dim(df4)
```