---
title: "STAT 33B Lecture Workbook Wk 10"
date: "Mar 28, 2021"
author: "Won Shil Park (3033452021)"
output: pdf_document
---

This workbook is due __Mar 31, 2021__ by 11:59pm PT.

* Knit and submit the generated PDF file on Gradescope.



Write a function that determines whether each element in a numeric vector is 
even or odd.

If all of the elements are even, `cat` the message `"All even"`. 

If they are all odd then `cat` the message `"All odd"`. 

Otherwise, `cat` the message, `"Mixed values, e.g. x is even and y is odd"` where `x` is an even value and `y` is an odd value of the input vector. 



```{r}
checkDivisibility = function(x) {
  rems = x %% 2
  z = sum(rems)
  
  if (z == 0) {
    cat("All even.\n")
  }
  if (z == length(x)) {
    cat("All odds.\n")
  }
  if (z > 0 & z < length(x)) {
    cat("Mixed values, e.g.,", x[which(rems == 0)[1]], "is even and",
        x[which(rems == 1)[1]], "is odd.\n")
  }
}

```


Test your function with the following inputs
```{r}
evens = seq(2, 10, by = 2)
odds = seq(1, 7, by = 2)
mixed = c(10, 12, 14, 17, 20)
```

```{r}
checkDivisibility(odds)
checkDivisibility(evens)
checkDivisibility(mixed)
```
